SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-10-11 scipy-1.0/paper.tex
Cleanup outline

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  SciPy is built on top of NumPy, and is itself the foundation
upon which higher level scientific libraries, including scikit-learn
and scikit-image, are built.

@@

\cite{vanderwalt2008scipy}
\cite{peterson2009f2py}
\cite{pedregosa2011scikit}
\cite{vanderwalt2014scikit}
\cite{meurer2017sympy}

FOSSEE
https://fossee.in/about-us

%\subsection*{SciKits}

% stefan, gael, david, jarrod, robert

website http://scikits.appspot.com/

statsmodels

scikit-learn

% scikits

% First scikit (mail moving over from nipy list?)
% https://mail.python.org/pipermail/scipy-dev/2007-March/006805.html

% First scikit development:
% https://mail.python.org/pipermail/scipy-dev/2007-April/006987.html

%https://mail.python.org/pipermail/scipy-dev/2006-November/006315.html
%https://mail.python.org/pipermail/scipy-dev/2006-November/006316.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006972.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006835.html

% roadmap
%https://mail.python.org/pipermail/scipy-dev/2007-March/006808.html

% scikit learn
%https://mail.python.org/pipermail/scipy-dev/2007-July/007451.html

@@

>>>>

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  SciPy is built on top of NumPy, and is itself the foundation
upon which higher level scientific libraries, including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.

@@

@@

sympy\cite{meurer2017sympy}

NetworkX\cite{hagberg2008networkx}
